Active Learning for SAT Solver Benchmarking

### 2024-05-24 paper_jar/paper.tex
section 6

In this work, we have addressed the \emph{New-Solver Problem}:
Given a new solver, we want to find its ranking amidst competitors.
Our approach provides accurate ranking predictions while needing significantly less runtime than a complete evaluation on a given benchmark set.
On data from the SAT~Competition~2022 Anniversary Track, we can determine a new solver's PAR-2 ranking with about \SI{92}{\%} accuracy while only needing \SI{10}{\%} of the full-evaluation time.
We have evaluated several ranking algorithms, instance-selection approaches, and stopping criteria within our sequential active-learning framework.
We also took a brief look at which instance families are the most prevalent in selection decisions.

Future work may compare further sub-routines for ranking, instance selection, and stopping.
Additionally, one can apply our evaluation framework to arbitrary computation-intensive problems, e.g., other $\mathcal{NP}$-complete problems than SAT, as all discussed active-learning methods are problem-agnostic.
Such problems share most of the relevant properties of SAT solving, i.e., there are established instance features, a complete benchmark is expensive, and traditional benchmark selection requires expert knowledge.

From the technical perspective, one could formulate runtime discretization as an optimization problem rather than addressing it empirically.
Further, a major shortcoming of our current approach is the lack of parallelization, selecting instances one at a time.
Benchmarking on a computing cluster with $n$ cores benefits from having batches of $n$ instances.
However, bigger batch sizes $n$ impede \emph{active learning}.
Also, it is unclear how to synchronize instance selection and updates of the prediction model without wasting too much runtime.

>>>>

In this work, we have addressed the \emph{New-Solver Problem}:
Given a new solver, we aim to determine its ranking relative to competitors.
Our approach provides accurate ranking predictions while requiring significantly less runtime than a complete evaluation on a given benchmark set.
On data from the SAT~Competition~2022 Anniversary Track, we can determine a new solver's PAR-2 ranking with about \SI{92}{\%} accuracy while only requiring \SI{10}{\%} of the full-evaluation time.
We have evaluated several ranking algorithms, instance-selection approaches, and stopping criteria within our sequential active learning framework.
We have also looked at which instance families are the most prevalent in selection decisions.

Future work could compare more sub-routines for ranking, instance selection, and stopping.
Our evaluation framework can be used for other computation-intensive problems, like other $\mathcal{NP}$-complete problems than SAT.
Such problems share most of the relevant properties of SAT, like established instance features, a complete benchmark is expensive, and traditional benchmark selection requires expert knowledge.

From a technical perspective, we could formulate the problem of runtime discretization as an optimization problem, rather than addressing it empirically.
Further, a major shortcoming of our current approach is the lack of parallelization, selecting instances one at a time.
Benchmarking on a computing cluster with $n$ cores benefits from having batches of $n$ instances.
However, bigger batch sizes $n$ impede \emph{active learning}.
Also, it is unclear how to synchronize instance selection and updates of the prediction model without wasting too much runtime.

In order to perform benchmarking on a computer cluster with multiple cores, it is necessary to have batches of multiple instances. This application demonstrates one of the principal limitations of our approach: it does not permit the concurrent execution of multiple instances, but rather necessitates the benchmarking of a single instance at a time.
In future work, we intend to investigate models that learn from partial labels, which can be extracted from larger batch sizes in a parallel approach that synchronizes instance selection and model updates.
